Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-10 paper-2024-sac-marl-neighbouring-strategies.tex
add scalability chart
commented figure on env

\subsection{Environment} 
First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
  called \emph{collect the items} -- see \Cref{fig:env}.
%
This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
 are randomly placed.
%
The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
%
In particular, each agent has an observation space defined by three main parameters, namely: 
\begin{enumerate*}[label=(\roman*)]
  \item number of closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
Regarding the action space, each agent has $8$ possible moves, namely the possible direction on a grid 
  (up, down and diagonal).

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\linewidth]{figures/env.pdf}
  \caption{Graphical representation of the environment. 
  Specifically, the environment consists of a 2D euclidean space.
  The blue dots represent the agents, while the yellow stars represent the items that 
  the agents aim to collect.
  }
  \label{fig:env}
\end{figure}

@@

>>>>

\subsection{Environment} 
First, we extended the \texttt{MultiAgentEnv} from RLlib to implement a custom cooperative environment 
  called \emph{collect the items}. % -- see \Cref{fig:env}.
%
This environment consists of a 2D euclidean space in which a variable number of \emph{items} and \emph{agents} 
 are randomly placed.
%
The goal of the agents is to cooperate to collect all the items in the smallest amount of time possible. 
%
In particular, each agent has an observation space defined by three main parameters, namely: 
\begin{enumerate*}[label=(\roman*)]
  \item number of closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
Regarding the action space, each agent has $8$ possible moves, namely the possible direction on a grid 
  (up, down and diagonal).

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.7\linewidth]{figures/env.pdf}
%   \caption{Graphical representation of the environment. 
%   Specifically, the environment consists of a 2D euclidean space.
%   The blue dots represent the agents, while the yellow stars represent the items that 
%   the agents aim to collect.
%   }
%   \label{fig:env}
% \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/scalability.pdf}
  \caption{ Communication overhead due to different neighboring strategies.
  }
  \label{fig:scalability}
\end{figure}
